US Korea Exchange Rates \\ STA206 Final Project

### 2014-12-14 paper.tex
merging exploratory files

    \item When is the best time to exchange currency from won (Korean
        currency) to dollar or vice versa?

@@

One other aspect of reproducibility is version control. In this
project we've used \texttt{Git} to collect snapshots of the project at
every stage. The project is hosted publicly on
Github\footnote{\url{https://github.com/clarkfitzg/stats206\_project}}.
A look at the log file shows what work happened when and why,
which is important for establishing provenance. In particular it shows 
that we've been active on this project every day since
December 1st. Here's an example of a log entry:

>>>>

    \item When is the best time to exchange currency from Korean Won
        to US Dollar or vice versa?

@@

One other aspect of reproducibility is version control. In this
project we've used \texttt{Git} to collect snapshots of the project at
every stage. The project is hosted publicly on
Github\footnote{\url{https://github.com/clarkfitzg/stats206\_project}}.
A look at the log file shows what work happened when and why,
which is important for establishing provenance. In particular it shows 
that we've been active on this project every day since
December 1st, pushed more than 30 commits, and wrote nearly 3000 lines of
code (including \LaTeX). Here's an example of a log entry:
